Alternatives for Neighborhood Function in Kohonen Maps \thanks{This work was supported by a private funding of Velbazhd Software LLC.}

### 2019-02-16 Alternatives-for-Neighborhood-Function-in-Kohonen-Maps/paper.tex
Small part of the introduction was written.

\keywords{Artificial neural networks\and Self-organizing maps \and Neighborhood functions.}
\end{abstract}

@@

>>>>

\keywords{Artificial neural networks \and Self-organizing maps \and Neighborhood functions.}
\end{abstract}

@@

Self-organizing maps or Kohonen Neural Networks (KNNs) are networks with unsupervised training. They are very useful in finding nonlinear dependencies when data are presented in very high dimensional spaces. The projection from the high-dimensional space is usually done in a rectangular lower-dimensional space. The main idea behind KNNs is the organization of unlabeled vectors with particular features in predefined number of groups called clusters.
